%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Education}

\cvevent{MS CS (Incoming Student)}{New York University}{Fall 2022}{Brooklyn, NY.}

\begin{itemize}
    \item MS CS @ Tandon School of Engineering.
\end{itemize}

\divider

\cvevent{B.Tech CSE}{Amrita Vishwa Vidyapeetham}{Jul 16 - Aug 20}{Amritapuri, India.}

\begin{itemize}
    \item GPA: 8.26/10.0
    \item Active member of amFOSS.
    \item GSoC 2020 with CHAOSS.
\end{itemize}

\divider

\cvevent{Summer School Program}{Ben-Gurion University of the Negev}{Jul - Aug, 2019}{Beersheba, Israel.}

\begin{itemize}
    \item Data Mining and BI with its applications in Cyber Security Summer course.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Languages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\cvsection{Languages}
\cvskill{English}{4}
\cvskill{Hindi/Telugu (Native)}{4}
\cvskill{Spanish}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Others %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% \cvsection{Others}
% \begin{itemize}
% \item Driving License -- B1/B
% \end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Skills}

\begin{itemize}
    \item \textcolor{emphasis}{Main Development Languages} 
\end{itemize}
\cvtag{Python}
\cvtag{Java}

\smallskip\smallskip

\begin{itemize}
    \item \textcolor{emphasis}{Frameworks} 
\end{itemize}
\cvtag{Django}
\cvtag{Flask}
\cvtag{React.js}

\smallskip\smallskip

\begin{itemize}
    \item \textcolor{emphasis}{Other Tools} 
\end{itemize}
\cvtag{SQL}
\cvtag{Docker}
\cvtag{Elastic Search}
\cvtag{Kibana}
\cvtag{AWS}
\cvtag{Jupyter}

\smallskip\smallskip

\begin{itemize}
    \item \textcolor{emphasis}{Soft Skills} 
\end{itemize}

\cvtag{Team Work}
\cvtag{Project Implementation}
\cvtag{Problem Solving}
\cvtag{Mentoring}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Additional Experience & Achievements %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Others}

\begin{itemize}
    % \item Conducted the Data Analytics with Python workshop as a part of the Road To Excellence program by CIR@Amrita in collaboration with amFOSS.
    % \item Served as the Student Coordinator for the Venue Maintenance Seva during Amritavarsham for four years.
    \item Served as the Student Coordinator during Amritavarsham which is the birthday celebration of Mata Amritanandamayi Devi, popularly known as "Amma".
    \item Got selected for the finals after finishing the Qualifier round of Amrita InCTF 2019, India’s First Capture the Flag Cyber security Contest.
\end{itemize}

